Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-14 docs/ms.tex
Update ms.tex

The prior distribution we used on $\vec{\alpha}$ is : 
\begin{equation}
p(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

@@

As described in the previous subsection we use the sample mean as the most probable $g_{i}$ and 
the standard deviation as the uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
most-likely value and uncertainty of m and c.

>>>>

The prior regularizer we used on $\vec{\alpha}$ is : 
\begin{equation}
p(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

@@

As described in section 3.1, we use the mean of posterior samples as the most probable $g_{i}$ and 
the standard deviation as uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
most-likely value and uncertainty of m and c.
